% arara: xelatex
% arara: xelatex

\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \bfseries Cole Gaboriault}

4048 Powelton Avenue\ \ \textbullet
\ \ Philadelphia, PA 19104
\\
(267) 809-0199\ \ \textbullet
\ \ cgabor@sas.upenn.edu
\end{center}


\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\bfseries University of Pennsylvania}
		{\bfseries Philadelphia, PA}
	\\
	\headerrow
		{Bachelor of Arts, \em Summa Cum Laude, Phi Beta Kappa, GPA: 3.99}
		{\em 2018 -- 2022}
	\\
	\headerrow
		{Physics, Linguistics, Classical Studies; Minors: Mathematics, Archaeological Science}{}

	\item
	\headerrow
		{\bfseries Penncrest High School}
		{\bfseries Media, PA}
	\\
	\headerrow
		{}
		{\em 2014 -- 2018}

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Work Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\bfseries Gregory College House}
		{\bfseries University of Pennsylvania}
	\\
	\headerrow
		{\em House Manager, Teaching Assistant}
		{\em 2021 -- 2022}
	Scheduled, coordinated, and ran events for residents of Gregory College House;
	led several weekly series of film screenings and discussions for the for-credit Film Culture Residential Program.

	\item
	\headerrow
		{\bfseries Mauger Group}
		{\bfseries University of Pennsylvania}
	\\
	\headerrow
		{\em Neutrino Physics Researcher}
		{\em Summer 2019}
	\\
	Used CERN's Geant4 toolkit in \CPP{} to develop accurate simulations of muon capture in water.

	\item
	\headerrow
		{\bfseries MedCrypt}
		{\bfseries www.medcrypt.co}
	\\
	\headerrow
		{\em Machine Learning Intern}
		{\em Summer 2016}
	\\
	Wrote a decision tree algorithm in Scala for identifying potentially malicious network activity.

	\item
	\headerrow
		{\bfseries ColdLight Solutions}
		{\bfseries Wayne, PA}
	\\
	\headerrow
		{\em Machine Learning Intern}
		{\em Summer 2015}
	\\
	Worked with a senior AI scientist to implement a new decision tree engine in Java.

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Achievements}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\bfseries Appalachian Trail}
		{\em March -- September 2023}
	Backpacked the 2,198.4 mile continous footpath from Springer Mountain, Georgia to Mount Katahdin, Maine.

	\item
	\headerrow
		{\bfseries 6abc Best in Class}
		{\em 2018}
	Selected by teachers and faculty to represent Penncrest High School at the annual 6abc Best in Class event.

	\item
	\headerrow
		{\bfseries National Conservation Foundation Envirothon}
		{\em 2017}
	Won first place individually and as a five-person team at the 2017 international NCF Envirothon after winning the Delaware County and Pennsylvania state competitions.

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Volunteering}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\bfseries Team Assist}
		{\em 2014 -- 2018}
	Provided tech support at Penncrest High School's student-run IT help desk;
	helped manage a small 3D printing business to raise funds.

	\item
	\headerrow
		{\bfseries Friends of Glen Providence Park}
		{\em 2011 -- present}
	Participated in citizen science projects, annual park cleanups, invasive plant removal,
	and annual National Public Lands Day plantings.

	\item
	\headerrow
		{\bfseries Delaware County Institute of Science}
		{\em 2014 -- present}
	Presented two lectures to the Junior DCIS Club, one to commemorate Pi Day and one tracing the history of physics through optics; assisted with various other projects including the accessioning of museum collections.

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Skills}

\begin{itemize}

	\item[]
	Programming languages: Java, Scala, POSIX Shell, HTML, CSS, C, \CPP{}

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Interests}

\begin{itemize}

	\item[]
	Stealing

\end{itemize}

\end{document}
}
